\thesistitle

### 2019-07-15 sections/research.tex
Detecting clones

@@

As stated in the previous section, nodes in the graph link to \textit{preceding} cloned statement. This implies that the first node that is cloned does not have any clone relation, as there are no clones preceding it (only following it). Because of this, we start our clone detection process at the final location encountered while building the graph. For this node, we collect all nodes it is cloned with. Even though the final node only links to the preceding node it is cloned with, we can collect all clones. This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node. As an example, see figure \ref{fig:clonegraph} and \label{fig:clonegraph2}.

@@

Using the example shown in figure \ref{fig:clonegraph} and \label{fig:clonegraph2} we can explain how we detect clones. Suppose we are finding clones for two files and the final node of the second file is a variable declarator. This final node is represented in the example figure by the purple box (1). We then follow all ``duplicate'' relations until we have found all clones of this node (2 and 3). We now have a single statement clone class of three clone instances (1, 2 and 3).

>>>>

\subsubsection{Mapping graph nodes to code}
The clone graph, as explained in section \ref{sec:buildingclonegraph}, contains all declarations and statements in a source code. However, declarations and statements may themselves have child declarations and statements. To avoid redundant duplication checks, we exclude child declarations and statements from each node. Look at figure \ref{fig:clonegraph} for an example of how source code maps to AST nodes.

@@

As stated in the previous section, nodes in the graph link to \textit{preceding} cloned statement. This implies that the first node that is cloned does not have any clone relation, as there are no clones preceding it (only following it). Because of this, we start our clone detection process at the final location encountered while building the graph. For this node, we collect all nodes it is cloned with. Even though the final node only links to the preceding node it is cloned with, we can collect all clones. This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node. As an example, we convert the code example shown in figure \ref{fig:clonegraph} to a clone graph as displayed in figure \label{fig:clonegraph2}.

@@

Using the example shown in figure \ref{fig:clonegraph} and \label{fig:clonegraph2} we can explain how we detect clones on basis of this graph. Suppose we are finding clones for two files and the final node of the second file is a variable declarator. This final node is represented in the example figure by the purple box (1). We then follow all ``duplicate'' relations until we have found all clones of this node (2 and 3). We now have a single statement clone class of three clone instances (1, 2 and 3).
